\textbf{CSDS 491: Assignment 4}

### 2021-04-22 A4/article.tex
🔨 Update E3.4 with more explaination.

>>>>

Note the magnitutde of the entries of each eigenvalues are similar, with the exception that the first eigenvector shows greater value on element \ilc{Fe}, the first eigenvector shows lesser value on element \ilc{Mg}, and the third eigenvector shows greater value on \ilc{RI} (the reflective index) -- suggesting that the classification of glass samples might be postively correlated to \ilc{Fe} and \ilc{RI}, and negatively correlated to \ilc{Mg}. In terms of co-vary between eigenvectors, it is hard to tell if there is much consistency.
